\documentclass{article}
\usepackage{epcc} 
\usepackage{graphicx}
\title{MSc in High Performance Computing \\
MSc in High Performance Computing with Data Science \\
Programming Skills Coursework \\
Contribution Questionnaire}
\author{NAME}
\begin{document}
\makeEPCCtitle

\section{Introduction}

This questionnaire summarises what you as an individual contributed to
the coursework and how you felt each member of the group
contributed. 

Only the markers will see these contribution questionnaires. 

\section{Your contribution}

Provide a brief summary of your contribution to each of these project
tasks e.g. did you set up the initial repository for revision control?
Which classes, modules or functions did you develop? Which sections of
the group report did you co-write? etc. 

Do not worry if you did not contribute to all tasks since this is a
simple fact of group-based work.

\begin{tabular}{|l|l|}
\hline
Task & Brief summary of contribution \\ 
\hline
\hline
Design & \\
\hline
Set up revision control & \\
\hline
Set up build tool & \\
\hline
Writing code & \\
\hline
Writing tests & \\
\hline
Performance testing & \\
\hline
Performance analysis & \\
\hline
Writing group report & \\
\hline
Other & \\
\hline
\end{tabular}

\section{Group contribution}

Provide a rating as to how you felt each member of the group, yourself
included, contributed to the course work:

\begin{tabular}{|l|l|l|l|l|l|}
\hline
Name & Exceptional & Above average & OK & Below average & Poor \\
\hline
\hline
You & & & & & \\
\hline
Group member 2 & & & & & \\
\hline
Group member 3 & & & & & \\
\hline
Group member 4 & & & & & \\
\hline
\end{tabular}

For yourself and for each group member, tick the box that you feel
most closely matches how you felt they contributed to the course work.

For cases where you do not tick ``OK'' provide an explanation of why
you feel this way: 

\section{Comments}

If you have any comments about how your group worked together, and any
problems encountered, then please add these here:

\end{document}
